Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-03-15 text/paper2/ms.tex
describe emcee add refs

We first test the model using eight stars sampled from the $2.5\times10^8~M_\odot$ simulation (Section~\ref{sec:sims}) --- four from the leading trail, and four from the trailing tail --- assuming perfect observational data for both the stars and the progenitor. The stars are additionally required to be within $50~kpc$ of the Sun. Figure~\ref{fig:} (left panel) shows a sample of stream particles (black) and the eight randomly chosen stars (blue) in the Galactic X-Z plane. We leave the potential parameters --- $q_1$, $q_z$, $\phi$, and $\vhalo$ --- free to vary, along with the Lagrange point offset, $\Loffset$, the tail assignment for each star, $\tailbit^{(i)}$, and probability that each star was shocked, $\pshock^{(i)}$. Figure~\ref{fig:} shows the posterior distribution for the four potential parameters, marginalized over the other parameters.

@@

@@

\acknowledgements
APW: NSF GRFP, Sigma Xi

>>>>

We first test the model using eight particles (stars) --- four from the leading trail, and four from the trailing tail --- randomly sampled from the $2.5\times10^8~M_\odot$ simulation (Section~\ref{sec:sims}), assuming perfect observational data for both the stars and the progenitor. The stars were required to have been stripped after the first pericentric passage and have a present-day distance within $50$ kpc of the Sun. Figure~\ref{fig:} (left panel) shows a sample of stream particles (black) and the eight randomly chosen stars (blue) in the Galactic X-Z plane.

We leave the potential parameters --- $q_1$, $q_z$, $\phi$, and $\vhalo$ --- free to vary, along with the Lagrange point offset, $\Loffset$, and use Markov Chain Monte Carlo (MCMC) to sample from the posterior probability distribution over these five parameters. In detail, we use an affine-invariant, ensemble sampler \citep{goodman10} implemented in the Python programming language \citep{foremanmackey13} with an ensemble of 64 walkers initialized by sampling from the priors summarized in Table~\ref{tbl:params}. We run the walkers in parallel (using MPI todo) for 5000 steps to burn-in, then restart the sampling starting from the final position of the burn-in phase and run for another 10000 steps. We compute the autocorrelation time for each parameter [todo: reference] and thin the chains by taking every XXX$\times \mathrm{median}(t_{\rm acor})$ sample to ensure they are close to independent. Figure~\ref{fig:} shows the walker positions over the 10000 post-burn-in steps for each parameter for the $2.5\times10^8~M_\odot$ simulation; the autocorrelation time for each parameter is displayed on each corresponding panel.

Figures~\ref{fig:}-\ref{fig:} show the posterior distributions for these five parameters for each of the the four mass progenitors.

@@

\subsection{Mass comparison}
[...]

@@

\acknowledgements
Aspen?\\
APW: NSF GRFP, Sigma Xi\\
Columbia HPC\\
